\documentclass{memoir}

\usepackage{enumerate}

\title{
Chapter 9: Exercises 3, 4
\\\vspace{2mm}
\large
A Technical Writing Assignment
}
\author{Connor Taffe}

\begin{document}
	\maketitle

Here follows the assigned homework for chapter 9.

\section{Exercise 3}

\subsection{Q.}

Exercise three asks the following:

\begin{quote}
	Revise the following list so that the lead-in is clear, easy to understand, and punctuated correctly. In addition, be sure the bullet items are grammatically parallel with one another.
\end{quote}

\subsection{A.}

The Natural and Accelerated Bioremediation Research office is currently pursuing several goals:

\begin{itemize}
	\item{
		Developing cost-effective \emph{in situ} bioremediation strategies for subsurface radionuclides and metals.
	}
	\item{
		Understanding intrinsic bioremediation as well as accelerated bioremediation using nutrient amendments to immobilize contaminants.
	}
	\item{
		Identifying societal issues associated with bioremediation research, and communication of bioremediation research findings to stakeholders.
	}
\end{itemize}

\section{Exercise 4}

\subsection{Q.}

Exercise four asks the following:

\begin{quote}
	Provide a topic sentence for each of the following paragraphs:

	\begin{enumerate}[a.]
		\item{
			The goal of the Web Privacy Project is to make it simple for users to learn the privacy practices of a Web site and thereby decide whether to visit the site. Site owners will electronically “define” their privacy practices according to a set of specifications. Users will enter their own preferences through settings on their browsers. When a user attempts to visit a site, the browser will read the site’s practices. If those practices match the user’s preferences, the user will seamlessly enter the site. However, if the site’s practices do not match the user’s preferences, the user will be asked whether he or she wishes to visit the site.
		}
		\item{
			The reason for this difference is that a larger percentage of engineers working in small firms may be expected to hold high-level positions. In firms with fewer than 20 engineers, for example, the median income was \$62,200. In firms of 20 to 200 engineers, the median income was \$60,345. For the largest firms, the median was \$58,600.
		}
	\end{enumerate}
\end{quote}

\subsection{A.}

\begin{enumerate}[a.]
	\item{
		Avoiding sites with disagreeable privacy policies could be simple.
	}
	\item{
		Engineers at smaller firms make on average nearly four thousand dollars more than those in larger firms.
	}
\end{enumerate}

\end{document}
